Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-07 arxiv-version/mistake-lower-bound-for-ignorant-algorithms.tex
Clean-up bibliography

\begin{lemma}
For any $\gamma \in (0,\frac 1 {160})$,
there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\label{lem:embed_d_gamma}
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

>>>>

\begin{lemma}
For any $\gamma \in (0,\frac 1 {160})$,
there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\label{lem:embed_d_gamma}
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long-1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

### 2019-01-07 arxiv-version/related-work.tex
Clean-up bibliography

Many works consider bandit multiclass classification in the general non-separable setting.
\cite{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
\cite{CrammerG13} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
\cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret
between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic loss, where the exact order of the regret depends on the diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret bound would become
$O(T^{2/3})$.
The SOBA algorithm by \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of $\tilde{O}(\sqrt{T})$ against the $\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}; in addition, their regret bound does not depend sensitively on the diameter of the benchmark class.
\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a regret of $\tilde{O}(\sqrt{T})$ against the multiclass logistic loss, where it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its dependence on the diameter of the benchmark class.
Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF} \frac 1 K \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$,
and $\phi(s) = \max(1 - \frac s \gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$.
On one hand, it gives information-theoretic mistake upper bounds under various settings of $\calF$, for instance parametric and nonparametric classes; On the other hand, it gives an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.

>>>>

Many works consider bandit multiclass classification in the general non-separable setting.
\cite{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
\cite{Crammer-Gentile-2013} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
\cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret
between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic loss, where the exact order of the regret depends on the diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret bound would become
$O(T^{2/3})$.
The SOBA algorithm by \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of $\tilde{O}(\sqrt{T})$ against the $\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}; in addition, their regret bound does not depend sensitively on the diameter of the benchmark class.
\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a regret of $\tilde{O}(\sqrt{T})$ against the multiclass logistic loss, where it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its dependence on the diameter of the benchmark class.
Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF} \frac 1 K \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$,
and $\phi(s) = \max(1 - \frac s \gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$.
On one hand, it gives information-theoretic mistake upper bounds under various settings of $\calF$, for instance parametric and nonparametric classes; On the other hand, it gives an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
